Decentralised location verification system

### 2016-04-01 presentation.tex
finishing presentation design section

	\begin{frame}
		\frametitle{Design}
		\framesubtitle{Transactions II}
		\begin{figure}[t]
			\resizebox {\columnwidth} {!} {\input{diagrams/transaction_presentation.tex}}
		\end{figure}
	\end{frame}
\end{document}

>>>>

	\begin{frame}
		\frametitle{Design}
		\framesubtitle{Transactions II}
		Node $A$ will create the following transaction after meeting node $B$:
		\newline

		\begin{center}
		\only<1>{$T_{An} = K_A(ts_A|loc_A|ID_{An}|KP_{Bm})$}
		\only<2->{$T_{An} = K_A(ts_A|loc_A|ID_{An}|\textcolor{red}{KP_{Bm}})$}
		\end{center}
	\end{frame}

	\begin{frame}
		\frametitle{Design}
		\framesubtitle{Transactions: Key Packets}
		Key Packets provide a Verifier with a means of examining a mobile node's transactions.
		\newline

		\only<2->{
		Two main properties:
		\begin{itemize}
			\only<2>{
			\item Allow a Verifier to build a tree of a mobile node's activity.
			}
			\only<3>{
			\item \textcolor{red}{Allow a Verifier to build a graph of a mobile node's activity.}
			}
			\item Allow a mobile node to preserve control its own privacy.
		\end{itemize}
		}
	\end{frame}

	\begin{frame}[b]
		\frametitle{Design}
		\framesubtitle{Transactions: Key Packets - Verification}
		\vspace{-0.5cm}
		\begin{figure}
			\resizebox {\columnwidth} {!} {\input{diagrams/tree.tex}}
		\end{figure}
	\end{frame}

	\begin{frame}
		\frametitle{Design}
		\framesubtitle{Transactions: Key Packets}
		Key Packets provide a Verifier with a means of examining a mobile node's transactions.
		\newline

		Two main properties:
		\begin{itemize}
			\item Allow a Verifier to build a graph of a mobile node's activity.
			\item \textcolor{red}{Allow a mobile node to preserve control its own privacy.}
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{Design}
		\framesubtitle{Transactions: Key Packets - Privacy}
		Published transactions split into two parts: Link and Transaction
		\newline

		\begin{figure}
			\resizebox {\columnwidth} {!} {\input{diagrams/link.tex}}
		\end{figure}
		\only<4->{
			\begin{center}
				Two \textit{Key Lists}: $KL_{AT}$ and $KL_{AL}$.
			\end{center}
		}
	\end{frame}

	\begin{frame}
		\frametitle{Design}
		\framesubtitle{Transactions III}
		Node $A$ will create the following transaction after meeting node $B$:

		\begin{center}
		\only<1>{$T_{An} = \textcolor{red}{K_A}(ts_A|loc_A|ID_{An}|KP_{Bm})$}
		\only<2>{$T_{An} = \textcolor{red}{KL_{AT}[n]}(ts_A|loc_A|ID_{An}|KP_{Bm})$}
		\only<3->{$T_{An} = KL_{AT}[n](ts_A|loc_A|ID_{An}|KP_{Bm})$}
		\end{center}
		\vspace{0.5cm}

		\only<3->{
		Node $A$ will then publish the following to the blockchain:

		\begin{center}
		$P_{An} = ID_{An}|\textcolor{red}{KL_{AL}[n]}(ID_{An-1}|ts_A)|T_{An}$
		\end{center}
		} 
	\end{frame}

	\begin{frame}
		\frametitle{Design}
		\framesubtitle{Verification}
		Mobile node needs to provide Verifier node with:
		\begin{itemize}
			\item ID of most recent transaction.
			\item Key Packet for $n$ most recent transactions.
			\item Nonce list for $n$ most recent IDs.
			\item Public key.
		\end{itemize}
	\end{frame}

\end{document}
